Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-10-25 ms/main.tex
added zefferman citation

Consider a large population whose members can be one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$. 
Following~\citet{ram2018evolution}, given that the parent phenotype is $\phi$ and assuming uni-parental inheritance, % TODO cite Zefferman Behav Ecol 2016
the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is

>>>>

Consider a large population whose members can be one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$. 
Following~\citet{ram2018evolution}, given that the parent phenotype is $\phi$ and assuming uni-parental inheritance~\citep{Zefferman2016}, the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
